A Formal Model of Checked C

### 2023-04-06 sandp23/introduction.tex
Adding all

One of the main reasons for this is combining partitioning with~\acf{SFI}.
Specifically, in addition to partitioning, existing techniques also provide~\ac{SFI} such that code in the untrusted region cannot affect code in the trusted region.\eg{} by executing untrusted partition in a separate process~\cite{liu2017ptrsplit} or executing in a Trusted Execution environment~\cite{lind2017glamdring}.
However, this extreme partitioning is not always necessary and feasible in certain resource constrained environments.
For instance, we want to isolate a string processing function only from spatial violations,~\ie any spatial violations (\eg buffer overread) in that function should not affect the program.

@@

>>>>

One of the main reasons for this is combining partitioning with~\acf{SFI}.
Specifically, in addition to partitioning, existing techniques also provide~\ac{SFI} such that code in the untrusted region cannot affect code in the trusted region,~\eg{} by executing untrusted partition in a separate process~\cite{liu2017ptrsplit} or executing in a Trusted Execution environment~\cite{lind2017glamdring}.
However, this extreme partitioning is not always necessary and feasible in certain resource constrained environments.
For instance, we want to isolate a string processing function only from spatial violations,~\ie any spatial violations (\eg buffer overread) in that function should not affect the program.

@@

In this paper, we present~\systemname{}, a Type Directed Flexible Program Partitioning system.
The main design principle of the system is to separate partitioning (\ie policy) from enforcing the separation between partitions (\ie mechanism).
Once a program is partitioned, users can choose enforcement mechanisms based on the desired guarantees and tolerable performance overhead. For instance, for the same program, the user may use complete~\ac{SFI} for desktop systems v/s isolation against only spatial safety issues on embedded systems.

We propose a type directed partitioning through untrusted types.
Specifically, we introduce~\textbf{tainted} (\taintt) qualifiers that can be used to annotate pointer types or functions. 
The tainted types form the untrusted partition or~\umode~\emph{region} (can only access tainted types), and the non-tainted types will be the trusted partition or~\cmode~\emph{region} (has complete access).
Through static type checking, our type system ensures that tainted types cannot directly affect untainted types.
After successful type checking,~\systemname{} creates two sets of source files~\ucregion{} and~\cregion{} containing tainted and untainted entities, respectively.

These sets of source files will be compiled using~\systemname{} compiler, which enforces the desired isolation through instrumentation.
Developers can choose a specific isolation mechanism.
We explore four different isolation mechanisms with varying guarantees and performance overhead (CITE SECTION).
For instance,~\isoheap{} provides safety against spatial and temporal violations of tainted pointers with almost no performance overhead.
Whereas~\sandbox{} isolation provides complete~\ac{SFI} with~\avgsandboxoverhead{} runtime overhead.

%Our dynamic instrumentation ensures that tainted pointer accesses are valid according to the desired isolation mechanism.
\noindent\textbf{Formal Guarantee.} We formally prove the~\emph{clean separation theorem} that guarantees that tainted types are isolated from the rest of the programs in a well-typed program.
The specific isolation guarantee depends on the target~\ac{SFI} mechanism.

In addition to the flexibility, the type based partitioning has the following advantages:

\noindent\textbf{Interactive Partitioning.} Our type system enables interactive partitioning, wherein developers start by annotating a risky pointer (\ie{} user data), and our type system will identify all the other additional pointers (depending on the tainted pointer) that need tainted or sanitized (\eg by explicitly copying to untainted buffer).

\noindent\textbf{Integrating with Other Mechanisms.} Using types enables us to integrate easily with existing type based safety mechanisms. We demonstrate this by combining~\systemname{} with~\checkedc, which we call~\ccflex.
\checkedc~\cite{Elliott2018} provides backward-compatible spatial safety by using checked pointer types. 
But, as we explain in~\sect{subsec:nosafetyagsintuncheckedcode}, the unchecked (or wild) pointers in a~\checkedc program are prone to cross-language attacks~\cite{mergendahl2022cross} and can violate the whole program's spatial safety.
However, using~\systemname{}, one can mark all unchecked (or wild) pointers as tainted, thus partitioning away unchecked types.
These unchecked components can be executed in an isolated sandbox, thereby preventing cross-language attacks and upholding~\checkedc guarantees.

Our evaluation shows that ---complete this. \aravind{Complete this.}

In summary following are our contributions:
